\chapter{ABSTRACT}

\indent\indent In the rapidly evolving landscape of Web3 social networks, such as Lens Protocol, detecting Sybil attacks remains a critical challenge for ensuring ecosystem integrity and trust. Traditional detection methods often struggle to capture complex, multi-layered interaction constraints and typically suffer from a severe lack of verified labels. This study proposes \textbf{SybilSignal}, a constraint-aware graph intelligence framework designed for explainable Sybil detection. The system models multi-dimensional social data into a four-layered relational graph—integrating follow, interact, similarity and co-owner constraints—enhanced by a logarithmic weight normalization mechanism to handle high-density network noise. A decoupled GNN-ML architecture is employed, utilizing an improved Graph Attention Network (GATv2) as a feature extractor combined with ensemble learning models for classification. Experimental results demonstrate that the GATv2 + Random Forest configuration achieves a state-of-the-art Macro F1-Score of 0.9303 on large-scale quarterly datasets. Notably, the model maintains a 0\% false positive rate for benign users, ensuring high reliability for practical deployment. By significantly reducing computational overhead through its decoupled design and providing clear behavioral insights, this research offers a scalable and transparent solution for maintaining security in decentralized social environments.\vspace{0.3cm}

\textbf{Keywords:} Sybil Detection, Web3 Social Graph, Graph Neural Networks, GATv2, Decoupled Architecture, Random Forest, SybilSignal.